Paper X

### 2023-01-13 output/paper/manuscript.qmd
Trying to fix qmd of manuscript without using lua filters

---
title: "Paper X"
author:
  - Lorenzo Fabbri:
      correspondence: "yes"
      email: "lorenzo.fabbri@isglobal.org"
      institute: [isg, upf]
institute:
  - isg: ISGlobal
  - upf: UPF
output:
  bookdown::pdf_document2:
    toc: no
    pandoc_args:
      - --filter=pandoc-crossref
      - --lua-filter=scholarly-metadata.lua
      - --lua-filter=author-info-blocks.lua
  bookdown::word_document: default
  bookdown::word_document2:
    pandoc_args:
      - --filter=pandoc-crossref
      - --lua-filter=scholarly-metadata.lua
      - --lua-filter=author-info-blocks.lua
      - --reference-doc=reference_document.docx
bibliography:
  - bibliography.bib
#csl: journal.csl
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage[switch, pagewise, running]{lineno}
  - \linenumbers
  - \renewcommand\linenumberfont{\normalfont\small}
  - \usepackage{rotating}
  - \usepackage{float}
abstract: |-
 \singlespacing
 **Background**

@@

 **Discussion**

  **Keywords:** Causal Inference
---

>>>>

---
title: "Paper X"
keywords:
  - Causal Inference
  - Epidemiology
author:
  - name: "Lorenzo Fabbri"
    number: 1
    email: lorenzo.fabbri@isglobal.org
    orcid: 0000-0003-3031-322X
    attributes:
      corresponding: true
    affiliations:
      - ref: isg
      - ref: upf
affiliations:
  - id: isg
    name: ISGlobal
    city: Barcelona
    state: Spain
  - id: upf
    name: UPF
    city: Barcelona
    state: Spain
format:
  pdf:
    pdf-engine: pdflatex
    toc: false
  # docx:
#csl: journal.csl
bibliography: bibliography.bib
link-citations: true
linkcolor: blue
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage[switch, pagewise, running]{lineno}
  - \linenumbers
  - \renewcommand\linenumberfont{\normalfont\small}
  - \usepackage{rotating}
  - \usepackage{float}
abstract: |
 \singlespacing
 **Background**

@@

 **Discussion**
---
